\vspace{-0.25em}\thetitle

### 2009-07-24 paper.tex
...

To see the linear structure of these representation matrices, we apply one of the most powerful tools of linear algebra:
the singular value decomposition (\caps{SVD}).
This matrix decomposition can be applied to any real matrix, factoring it into a product of three real matrices:
\begin{align}
  X = U\!S\trans{V}.
\end{align}
$U$ and $V$ are orthogonal and $S$ is diagonal, with entries of nonincreasing nonnegative value.
Among the useful properties of this factorization, is that the first $k$ columns of $U\!S$ are an optimal $k$-dimensional reduced model of $X$.\svdnote
This property allows us to visualize the structure of $X$ using initial columns of $U\!S$.
However, we are interested only interested in direction since
vectors differing only by magnitude lie in the same one-dimensional subspace.
To visualize direction while eliminating distance, we project all data points onto the unit-sum hyperplane through the origin.\projectionnote

\Figure{svd} illustrates the results of applying \caps{SVD} dimension reduction to sample matrices of six different traffic traces.
The figures show scatter plots of the most significant two projected \caps{SVD} coordinates for a matrix of 5000 sample flows from each trace.
% The original data encodes packet size distributions, inter-packet interval distributions, \caps{IP} protocol numbers, and port numbers for a sample of 5000 flows from each trace.
% The exact details of how the linear representation encodes these features will be discussed in \Section{methodology}.
Linear structure is visible in all six:
flow behaviors are heavily concentrated near low-dimensional subspaces.
Points concentrated along a one-dimensional subspace appear as dark ``spots'' where many points have been plotted;
points concentrated near two-dimensional subspaces appear as lines;
points falling along higher subspaces appear as ``smears.''
% There is a smattering of outliers, not especially near such structures.

The presence of linear structure in the matrix representations of several independent traffic traces immediately raises two significant questions.
The more philosophical question is \emph{Why does this linear structure exist?}
The more practical question is \emph{How can we exploit this structure?}
Neither question can be answered fully in a single paper.
In what follows, we provide some insight into the first question, and use that insight to predict the behavior of individual flows from the observation of only a few initial packets.

@@

>>>>

To see the linear structure of these representation matrices, we apply one of the most powerful tools of linear algebra:
the singular value decomposition (\caps{SVD}).
This matrix decomposition can be applied to any real matrix, factoring it into a product of three real matrices:
\begin{align}
  X = U\!S\trans{V}.
\end{align}
$U$ and $V$ are orthogonal and $S$ is diagonal, with entries of nonincreasing nonnegative value.
Among the useful properties of this factorization, is that the first $k$ columns of $U\!S$ are an optimal $k$-dimensional reduced model of $X$.\svdnote
This property allows us to visualize the structure of $X$ using initial columns of $U\!S$.
However, we are interested only interested in direction since
vectors differing only by magnitude lie in the same one-dimensional subspace.
To visualize direction while eliminating distance, we project all data points onto the unit-sum hyperplane from the origin.\projectionnote

\Figure{svd} illustrates the results of applying \caps{SVD} dimension reduction to sample matrices of six different traffic traces.
The figures show scatter plots of the most significant two projected \caps{SVD} coordinates for a matrix of 5000 sample flows from each trace.
% The original data encodes packet size distributions, inter-packet interval distributions, \caps{IP} protocol numbers, and port numbers for a sample of 5000 flows from each trace.
% The exact details of how the linear representation encodes these features will be discussed in \Section{methodology}.
Linear structure is visible in all six:
flow behaviors are heavily concentrated near low-dimensional subspaces.
Behaviors concentrated along a one-dimensional subspace appear as dark ``spots'' where many points have been plotted;
behaviors near two-dimensional subspaces appear as lines;
behaviors on higher-dimensional subspaces appear as ``smears.''
% There is a smattering of outliers, not especially near such structures.

The presence of linear structure in the matrix representations of several independent traffic traces immediately raises two significant questions.
The existential question: \emph{Why does this linear structure exist?}
Followed, of course, by the practical question: \emph{How can we exploit this structure?}
Neither question can be answered fully in a single paper, but we will begin to address the existential problem now.
In the rest of the paper we apply this insight to the eminently practical problem of predicting the behavior of individual flows from the observation of only a few of their initial packets.

@@

\subsection{Linear Representation}\sec{linear-representation}

\subsection{Subspace Segmentation}\sec{subspace-segmentation}

\subsection{Subspace Factorization}\sec{subspace-factorization}

\subsection{Flow Behavior Prediction}\sec{flow-behavior-prediction}
